\begin{acknowledgements}
This bachelor thesis is conducted at Institut fuer Informationsverarbeitung, Leibniz Universitaet Hannover, Germany during three and a half month's time from Feb, 24th to May, 23rd, 2017. This research is based on Ren Li's bachelor thesis. He has graduated from University of Science and Technology of China(USTC) with a bachelor's degree in 2016. 

At first, I would like to thank my advisor Felix Kuhnke(M.Sc.) for his technical assistance as well as his help in dataset collection. At the same time, I would also like to say thank you to my supervisor Prof. Joern Ostermann(Prof. Dr.-Ing), whose strong academic background and rigorous scientific attitude influenced me greatly. 

What's more, I really appreciate Prof. Zhibo Chen's guidance and help not only during the time working on my bachelor thesis but also the time when I conducted the researches concerning fatigue detection. It is Prof. Chen who gave me a chance to learn more about research ethics and scientific methods.

Besides, I want to express my gratitude to the bachelor student from USTC, Yichen Wang, who has volunteered to be the subject of my data collection experiment. I am really thankful for his cooperation.
Last but not least, I would like to say thank you to USTC from my bottom heart. It is USTC that offers me various opportunities to improve myself and make me qualified to pursue further education overseas. I really appreciate my four-year time here and it would be treasured in my whole life.









%在研究学习期间，我有幸得到了三位老师的教导，
%他们是：我的导师，中国科大XXX研究员，中科院X昆明动物所马老师以及美国犹他大学的XXX老师。
%三位深厚的学术功底，严谨的工作态度和敏锐的科学洞察力使我受益良多。
%衷心感谢他们多年来给予我的悉心教导和热情帮助。

%感谢XXX老师在实验方面的指导以及教授的帮助。
%科大的XXX同学和XXX同学参与了部分试验工作，在此深表谢意。

\end{acknowledgements}
